### 2011-02-10 paper/results.tex
minor fix

\acmFiggggg{explore_dim_1}{explore_dim_2}{explore_dim_3}{explore_dim_4}{explore_dim_5}{1}{.5}{Fitness
  mean and standard deviation vs. dimension 5.  The circle is a common
  point in \figref{explore_dim_1} through \figref{explore_dim_5}}

>>>>

\acmFiggggg{explore_dim_1}{explore_dim_2}{explore_dim_3}{explore_dim_4}{explore_dim_5}{1}{.53}{Fitness
  mean and standard deviation when each parameter dimension is varied
  independently.  The red triangle is the intersection of the slices
  along each dimension and is common to all plots.}
